\documentclass[12pt, openany, oneside, a4paper, english, brazil]{abntex2}   % Padrão Abntex2

\input{style/packages.tex} % resto dos pacotes Latex
%\usepackage[english]{style/UFSC-ECA-Monograph} % personalização da ABNTEX2 para escrita em inglês  
\usepackage[english]{style/UFSC-ECA-Monograph} % personalização da ABNTEX2 para escrita em português


%---------------------------------------------------------------
%--------- DADOS BÁSICOS DO TRABALHO (Preencher todos) ---------
%---------------------------------------------------------------


\titulo{Comparação e \textit{benchmarking} para SLAM em robôs móveis: \\ Um estudo de caso em robôs assistivos}   % Título do Trabalho em Português
\tituloingles{Comparison and benchmarking for SLAM in mobile robots: \\ A case study in assistive robots}   % Título do Trabalho em Inglês

\DEELautor{Brunno}{Vanelli} % Aluno autor do trabalho

\curso{Engenharia de Controle e Automação}											
\orientador{Prof. Dr. Marcelo Roberto Petry}  % Professor Orientador membro da banca 

\membrob{Prof. Dr. Leonardo Mejia Rincon}   % Professor membro da banca 
\membroc{Prof. Dr. Ciro André Pitz}   % Professor membro da banca

\local{Blumenau}   % Cidade da instituição
\data{2019}        % Ano de realização


%--------------------------------------------------------------------------------------------



\begin{document}
% Seleção automática do idioma, não alterar
\ifx\isenglish\undefined
    \selectlanguage{brazil}
\else
    \selectlanguage{english}
\fi

% Texto da Dedicatória (OBS: dedicatória é opcional)
% Caso não queira inserir, deixe em branco ( \dedicatoria{} )
\DEELdedicatoria{Don't panic.}

% Texto dos Agradecimentos (OBS: Agradecimentos é opcional)
% Caso não queira inserir, deixe em branco ( \agradecimentos{} )
\DEELagradecimentos{It is always hard to find words to acknowledge all the people that were and are important during all these years. If I happen to forget anyone, Sir or Madam, truly your forgiveness I implore.

I want to first thank my parents Augustinho and Isabel, and my sister Jaquelline, for supporting me for all these years I've been an unproductive member of society (hopefully that will end soon).

To my close friends for sharing laughs and eventually food during 5 long years.

To Gabriela for all unlicensed psychological support provided to each other.

To all my professors at UFSC who dedicate their lives to transmit their knowledge forward. A special thanks to professor Marcelo Roberto Petry who oriented me during this dissertation even when far away.

To my supervisors and colleagues at Fraunhofer IPA that during my internship allowed me to learn so much about robotics and got me fascinated on the field.

To all the people I met in the weirdest of circumstances in Stuttgart area and around the world, making my stay a lot better and giving me the opportunity to learn many different cultures. To the survival machine that showed me not all genes are selfish.

And finally, to the open-source community, without whom this work wouldn't be possible. In their free time, they coded the operating system I was working on, the framework that I was working on, the tools and used and even helped me solve the bugs in my code I didn't even know I had.
}
    
                                  
% Texto da Epígrafe (OBS: Epígrafe é opcional)
% Caso não queira inserir, deixe em branco ( \epigrafe{} )
\DEELepigrafe{\textit{"Did you ever hear the tragedy of Darth Plagueis the Wise?\\ I thought not. It's not a story the Jedi would tell you.\\ It's a Sith legend. Darth Plagueis was a Dark Lord of the Sith, so powerful and so wise he could use the Force to influence the midichlorians to create life...\\ He had such a knowledge of the dark side that he could even keep the ones he cared about from dying.\\ The dark side of the Force is a pathway to many abilities some consider to be unnatural.\\ He became so powerful... the only thing he was afraid of was losing his power, which eventually, of course, he did.\\ Unfortunately, he taught his apprentice everything he knew, then his apprentice killed him in his sleep.\\ It's ironic he could save others from death, but not himself."} \\ (Sheev Palpatine)} 
    

% Texto do Resumo (OBS: Resumo é Obrigatório)
%xxx
%O resumo deve apresentar os seguintes itens, nesta ordem:
%*Descrição do tópico abordado
%*A principal questão ou hipótese 
%*A abordagem utilizada para responder à questão
%*Os principais resultados e dados
%*Uma conclusão sobre o que foi descoberto
% Texto do Abstract (OBS: Abstract é Obrigatório)
\input{abstract.tex}



%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Elementos Pré-Textuais%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ElementosPreTextuais
% Insere todos os elementos Pré-Textuais listados (capa, folha de rosto, ...)
    % capa                   % Obrigatório
    % folhaderosto           % Obrigatório
    % folhaaprovacao         % Obrigatório
	% dedicatoria            % Opcional
	% agradecimentos         % Opcional
    % epigrafe               % Opcional
    % resumo                 % Obrigatório
    % abstract               % Obrigatório
\
%\newpage
%--------Lista de figuras--------
\ListaDeFiguras 
%--------Lista de tabelas--------
\ListaDeTabelas 
%--------Lista de Siglas e Abreviaturas--------
\include{list_siglas}   
%--------Lista de Simbolos e Notação--------
%\include{list_simbolos} 
%--------Sumário-------
\Sumario


%%%%%%%%%%%%%%%%%%%%%%
%%Elementos Textuais%%
%%%%%%%%%%%%%%%%%%%%%%
\textual 
\include{capitulos/1_introducao}
\include{capitulos/2_fundamentacao}
\include{capitulos/3_desenvolvimento}
\include{capitulos/4_resultados}
\include{capitulos/5_conclusoes}



%%%%%%%%%%%%%%%%%%%%%%%%%%
%%Elementos Pós-Textuais%%
%%%%%%%%%%%%%%%%%%%%%%%%%%
%%--------Bibliografia--------
\Bibliografia{bibliografia} % arquivo bibtex com as referências (referenciasbibliograficas.bib)

%%--------Apêndice--------
%% Descomente caso exista a necessidade da inclusão de apêndices
%\apendice % Comando que inclui os apêndices
%\include{7_Apendice/apendice_1}   % Arquivo apendice_1.tex
%\include{7_Apendice/apendice_2}   % Arquivo apendice_2.tex
%%---------------------------------------------------------------

%%--------Anexos-------------------------------------------------
%% Descomente caso exista a necessidade da inclusão de anexos
%\anexo % Comando que inclui os anexos (outros autores)
%\include{8_Anexos/anexo_1}  % Arquivo anexo_1.tex
%\include{8_Anexos/anexo_2}  % Arquivo anexo_2.tex
%%---------------------------------------------------------------

\end{document}
